---
title: "UNUSED"
author: "Maureen Anne Williams"
date: "11/27/2019"
output: html_document
---
This is a set of code that can be called the "candybag"- a name taken from the writers of "The Good Place". This code was either broke, not used in final analyses, or a path that didn't go anywhere. It's saved just in case it's ever needed again or if the syntax can be helpful. Don't use it unless you are desperate, and please don't judge me on its merits. :)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

#############
#STUFF NOT TO USE BECAUSE IT IS bad.
#generate general plots for lanesborough and shannonbridge

theme_set(theme_bw())#removes background colours on ggplot
#lanesborough colour palatte generation
lbPalette<-c("#009E73", "#F0E442", "#D55E00", "#CC79A7")

lanesborough<-ggplot(temp_horiz, aes(x=date_time_R)) + #generate overall plot
  geom_line(aes(y=LB_T1, col="T1")) +  #add line for T1
  geom_line(aes(y=LB_T3, col="T3")) + #add line for T3 Top
  geom_line(aes(y=LB_T6HOT, col="T6 Hot")) + #add line for T6 Cold
  geom_line(aes(y=LB_T6C, col="T6 Cold")) + #add line for T6 Hot
  scale_colour_manual(values=lbPalette)+ #change line colours
  coord_cartesian(ylim=c(0,30))+ #adjust y axis
  guides(colour = guide_legend(override.aes = list(size=3)))+ #make lines in legend thicker
  theme(plot.title = element_text(hjust = 0.5))+ #center overall title
  labs(title="Lanesborough Temperature",  
       x="", y="Temperature °C", colour="Logger") #labels

#shannonbridge colour palatte generation
sbPalette <- c("#000000", "#E69F00", "#56B4E9", "#FF3333")

shannonbridge<-ggplot(temp_horiz, aes(x=date_time_R)) + #generate overall plot
  geom_line(aes(y=SB_S1, col="S1")) + #add line for s1
  geom_line(aes(y=SB_S2, col="S2")) + #add line for s2
  geom_line(aes(y=SB_S3, col="S3")) + #add line for s3
  geom_line(aes(y=SB_S4, col="S4")) + #add line for s4
  scale_colour_manual(values=sbPalette)+ #change line colours
  coord_cartesian(ylim=c(0,30))+ #adjust y axis
  scale_x_date( limits= c(as.Date("2017/07/15"), as.Date("2018/03/18")))+#adjust x axis
  guides(colour = guide_legend(override.aes = list(size=3)))+ #make lines in legend thicker
  theme(plot.title = element_text(hjust = 0.5))+ #center overall title
  labs(title="Shannonbridge Temperature",  
       x="", y="Temperature °C", colour="Logger") #labels

multiplot(lanesborough,shannonbridge, cols=1) #print plots on same page

byday_summary$date <- as.Date(with(byday_summary, paste(year, mm, dd,sep="-")), "%Y-%m-%d")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

ggplot(byday_summary, aes(x=mmddyy)) + #generate overall plot
  geom_point(aes(y=mean, colour = factor(transect_id))) + #add lines
  geom_smooth(aes(y=mean, colour = factor(transect_id))) +
  coord_cartesian(ylim=c(0,30))+ #adjust y axis
  scale_colour_manual(values=cbbPalette, labels=c("LA3", "LH3", "LA2", "LH2","SA3","SH3", "SA2", "SA1"))+
  theme(axis.text=element_text(size=14, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        legend.title=element_text(size=14),
        legend.text=element_text(size=12),
        panel.grid.major = element_blank(), 
        plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank(),panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))+ #center overall title
  labs(x="", y="Mean Daily Temperature °C", colour="Site") #labels


temp_long$growth1[temp_long$temp >= 10 & temp_long$temp <= 35] <- "1"
temp_long$growth1[is.na(temp_long$growth1)] <- 0

temp_long$toohot[temp_long$temp >= 28] <- "1"

temp_long$toohot[is.na(temp_long$toohot)] <- 0

temp_long$larvae1[temp_long$temp >= 15 & temp_long$temp <= 28] <- "1"
temp_long$larvae1[is.na(temp_long$larvae1)] <- 0

toohot_summary<- ddply(temp_long, c("transect_id"), summarise,
                       N    = length(toohot),#number of 10 minute intervals
                       toohotsum = sum(toohot=="1",na.rm=T), #number of larvae intervals
                       non = sum(toohot=="0"),#number of no larvae intervals
                       propoftime   = (toohotsum / N))

larvae_summary<- ddply(temp_long, c("transect_id"), summarise,
                       N    = length(larvae),#number of 10 minute intervals
                       larvae = sum(larvae=="1",na.rm=T), #number of larvae intervals
                       non = sum(larvae=="0"),#number of no larvae intervals
                       propoftime   = (larvae / N)) 

growth_summary<- ddply(temp_long, c("transect_id"), summarise,
                       N    = length(growth1),#number of 10 minute intervals
                       growth = sum(growth1=="1",na.rm=T), #number of larvae intervals
                       notgrowth   = sum(growth1=="0",na.rm=T),#number of no larvae intervals
                       check = sum(growth+notgrowth),
                       propoftime   = growth / N) 

super_summary<-ddply(temp_long, c("transect_id"), summarise,
                     N    = length(mmddyy),#number of intervals per day
                     growth_sum = sum(growth1=="1",na.rm=T), #number of growth optimum intervals
                     larvae_sum   = sum(larvae1=="1",na.rm=T),#number of larval release intervals
                     measuredminutes = N*10, #minutes measured in the transect
                     growth_minutes = growth_sum*10, #minutes at growth optimum
                     larvae_minutes = larvae_sum*10, #minutes for potential larval release
                     growth_prop = growth_minutes/measuredminutes,
                     larvae_prop = larvae_minutes/measuredminutes
)

daily_summary<-ddply(temp_long, c("mmddyy","transect_id"), summarise,
                     N    = length(mmddyy),#number of intervals per day
                     growth_sum = sum(growth1=="1",na.rm=T), #number of growth optimum intervals
                     larvae_sum   = sum(larvae1=="1",na.rm=T))#number of larval release intervals

daily_summary$growth_binary[daily_summary$growth_sum>=1] <- 1
daily_summary$growth_binary[is.na(daily_summary$growth_binary)] <- 0
daily_summary$larvae_binary[daily_summary$larvae_sum>=1] <- 1
daily_summary$larvae_binary[is.na(daily_summary$larvae_binary)] <- 0

day_totals<-ddply(daily_summary, c("transect_id"), summarise,
                  N    = length(mmddyy),#number of intervals per day
                  larval_days = sum(larvae_binary==1,na.rm=T),
                  growth_days = sum(growth_binary==1,na.rm=T)
) #number of growth optimum intervals



########
#Summary Stats for the two areas 
N_LB<-length(temp_horiz$LB_diff) #Number of points
mean_LB<- mean(temp_horiz$LB_diff,na.rm=T) #Lanesborough Mean
sd_LB<- sd(temp_horiz$LB_diff,na.rm=T) #Lanesborough Standard Deviation
se_LB<- sd_LB / sqrt(N_LB) #Lanesborough Standard Error

N_SB<-length(temp_horiz$SB_diff) #Number of points
mean_SB<- mean(temp_horiz$SB_diff,na.rm=T) #Shannonbridge Mean
sd_SB<- sd(temp_horiz$SB_diff,na.rm=T) #Shannonbridge Standard Deviation
se_SB<- sd_SB / sqrt(N_SB) #shannonbridge Standard Error



byhour_summary <- ddply(temp_long, c("mm", "dd", "year","hour","transect_id"), summarise,
                       N    = length(temp),
                       mean = mean(temp,na.rm=T),
                       sd   = sd(temp,na.rm=T),
                       se   = sd / sqrt(N))
t6hot_gdd<-GDD(byhour_summary$mean[byhour_summary$transect_id=="LB_T6H"],summ=FALSE,Tbase=16)
t6hot_gdd[t6hot_gdd < 0] <- 0 
sum(t6hot_gdd)
t6cold_gdd<-GDD(byhour_summary$mean[byhour_summary$transect_id=="LB_T6C"],summ=FALSE,Tbase=16)
t6cold_gdd[t6cold_gdd < 0] <- 0 
sum(t6cold_gdd)



```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
